SecFFT: Safeguarding Federated Fine-tuning for Large Vision Language Models against Covert Backdoor Attacks in IoRT Networks

### 2024-11-02 response.tex

% \begin{algorithm}
% \caption{Instantaneous Attack Behavior Perception}
% \label{alg:malicious-node-detection}
% \begin{algorithmic}[1]
% \State \textbf{Input:} $d$, $N$, $(\triangledown \theta_0^t, \triangledown \theta_1^t, \ldots, \triangledown \theta_N^t) \in \mathbb{R}^{N \times d}$, $m$ \Comment{$d$ is the dimension of each update; $N$ is the number of nodes participating during each round; $(\triangledown \theta_0^t, \triangledown \theta_1^t, \ldots, \triangledown \theta_N^t) \in \mathbb{R}^{N \times d}$ is the local updates from robot nodes during the $t$-th round; $m$ is the length of low-frequency components}
% \State \textbf{Output:} $U_{nor}$, $U_{mal}$ \Comment{benign nodes, malicious nodes}
% \State{\color{CadetBlue}/* \textbf{Frequency Domain Transformation */}} 
% % \State Step 1: Frequency Domain Transformation
% \For {$R_i \in \textcolor{blue}{\{R_1, \ldots, R_N\}}$}
%     \State \textcolor{blue}{$G_i^t \gets Trunc(DCT(Flatten(\triangledown \theta_i^t))), m)$}
% \EndFor

% % \State
% \State{\color{CadetBlue}/* \textbf{Clean Ingredient Extraction */}} 
% % \State Step 2: Clean Ingredient Extraction
% \State $(C_0^t, C_1^t, \ldots, C_{\kappa}^t) \gets Clustering\textcolor{blue}{ (G_0^t, G_1^t, \ldots, G_N^t)}$ \Comment{$\kappa$ denotes the number of clusters}
% \State \textcolor{blue}{$ C^t_{max} \gets \underset{C^t_j}{\arg\max} \, |C^t_j|$ \Comment{$|C^t_j|$ denotes the number of nodes in cluster $C^t_j$, $j = 1, 2, \ldots, \kappa $}}
% \State $H^t \gets (G^t_{i_0}, G^t_{i_1}, \ldots, G^t_{i_n}) \in \mathbb{R}^{m \times n} $ \Comment{Stacking to form Matrix $H^t$, where $R_{i_0}, R_{i_1}, \ldots, R_{i_n} \in C^t_{max}$.}

% \State $\hat{H}^t \gets (H^t)^{T} H^t$
% \State $\lambda_{max}^t, \xi_{max}^t \gets eig(\hat{H}^t)$ \Comment{Calculating the maximum singular value and its corresponding eigenvector}
% \State $\tilde{G}^t \gets \frac{H^t \xi_{max}^t}{\sqrt{\lambda_{max}^t}}$ \Comment{The clean ingredient}

% % \State
% \State{\color{CadetBlue}/* \textbf{Chi-square distance calculation */}} 
% % \State Step 3: Chi-square distance calculation
% % \State $P_i^t \gets Softmax(G_i^t), \, Q^t \gets Softmax(\tilde{G}^t)$
% \For {$R_i \in \textcolor{blue}{\{R_1, \ldots, R_N\}}$}
% \State \textcolor{blue}{$Chi^t_i \gets \sqrt{\sum_{k=0}^{m-1}\frac{(G_i^t[k] - {\tilde G}^t[k])^2}{{|\tilde G}^t[k]| + \epsilon}}$}
% \EndFor
% \State \textcolor{blue}{$S^t \gets \{Chi^t_1, Chi^t_2, \ldots, Chi^t_N\}$} \Comment{The Distance differences calculated by Chi-square distance.}

% % \State
% \State{\color{CadetBlue}/* \textbf{Single-round malicious behavior perception */}} 
% % \State Step 4: Single-round malicious behavior perception
% \State $\textcolor{blue}{\{{C^t_1}', {C^t_2}'\}} \gets KMeans(S^t, 2)$ \Comment{Cluster $S$ into 2 clusters using KMeans.}
% \State \textcolor{blue}{$U_{nor} \gets C'_{max}$, $U_{mal} \gets \{C'_i \, | \, i \neq max\}$}

% \end{algorithmic}
% \end{algorithm}

\begin{algorithm}
\caption{Instantaneous Attack Behavior Perception}
\label{alg:malicious-node-detection}
\begin{algorithmic}[1]
\State \textbf{Input:} $d$, $N$, $(\triangledown \theta_0^t, \triangledown \theta_1^t, \ldots, \triangledown \theta_N^t) \in \mathbb{R}^{N \times d}$, $m$ \Comment{$d$ is the dimension of each update; $N$ is the number of nodes participating during each round; $(\triangledown \theta_0^t, \triangledown \theta_1^t, \ldots, \triangledown \theta_N^t) \in \mathbb{R}^{N \times d}$ is the local updates from robot nodes during the $t$-th round; $m$ is the length of low-frequency vector}
\State \textbf{Output:} $U_{nor}$, $U_{mal}$ \Comment{benign nodes, malicious nodes}
\State{\color{CadetBlue}/* \textbf{Frequency Domain Transformation */}} 
% \State Step 1: Frequency Domain Transformation
\For {$R_i \in \textcolor{blue}{\{R_1, \ldots, R_N\}}$}
    \State \textcolor{blue}{$G_i^t \gets Trunc(DCT(Flatten(\triangledown \theta_i^t))), m)$}
\EndFor

@@

% \State
\State{\color{CadetBlue}/* \textbf{Clean Ingredient Extraction */}} 
% \State Step 2: Clean Ingredient Extraction
\State $(C_0^t, C_1^t, \ldots, C_{\kappa}^t) \gets Clustering\textcolor{blue}{ (G_0^t, G_1^t, \ldots, G_N^t)}$ \Comment{$\kappa$ denotes the number of clusters}
\State \textcolor{blue}{$ C^t_{max} \gets \underset{C^t_j}{\arg\max} \, |C^t_j|$ \Comment{$|C^t_j|$ denotes the number of nodes in cluster $C^t_j$, $j = 1, 2, \ldots, \kappa $}}
\State $H^t \gets (G^t_{i_0}, G^t_{i_1}, \ldots, G^t_{i_n}) \in \mathbb{R}^{m \times n} $ \Comment{Stacking to form Matrix $H^t$, where $R_{i_0}, R_{i_1}, \ldots, R_{i_n} \in C^t_{max}$.}

\State $\hat{H}^t \gets (H^t)^{T} H^t$
\State $\lambda_{max}^t, \xi_{max}^t \gets eig(\hat{H}^t)$ \Comment{Calculating the maximum singular value and its corresponding eigenvector}
\State $\tilde{G}^t \gets \frac{H^t \xi_{max}^t}{\sqrt{\lambda_{max}^t}}$ \Comment{The clean ingredient}

% \State
\State{\color{CadetBlue}/* \textbf{Chi-square distance calculation */}} 
% \State Step 3: Chi-square distance calculation
% \State $P_i^t \gets Softmax(G_i^t), \, Q^t \gets Softmax(\tilde{G}^t)$
\For {$R_i \in \textcolor{blue}{\{R_1, \ldots, R_N\}}$}
    \State \textcolor{blue}{$Chi^t_i \gets \sqrt{\sum_{k=0}^{m-1}\frac{(G_i^t[k] - {\tilde G}^t[k])^2}{|{\tilde G}^t[k]| + \epsilon}}$}
\EndFor
\State \textcolor{blue}{$S^t \gets \{Chi^t_1, Chi^t_2, \ldots, Chi^t_N\}$} \Comment{The Distance differences calculated by Chi-square distance.}

@@

\multirow{4}{*}{\textcolor{blue}{Angle}} & \textcolor{blue}{Foolsgold} & \textcolor{blue}{0.88} & \textcolor{blue}{0.73} & \textcolor{blue}{0.06} & \textcolor{blue}{0.27} & \textcolor{blue}{0.84} & \textcolor{blue}{0.68} \\ 
                       & \textcolor{blue}{FLTrust}   & \textcolor{blue}{0.86} & \textcolor{blue}{0.60} & \textcolor{blue}{0.03} & \textcolor{blue}{0.40} & \textcolor{blue}{0.80} & \textcolor{blue}{0.65} \\ 
                       & \textcolor{blue}{Flame}     & \textcolor{blue}{0.90} & \textcolor{blue}{0.67} & \textbf{\textcolor{blue}{0.00}} & \textcolor{blue}{0.33} & \textcolor{blue}{0.83} & \textcolor{blue}{0.76} \\ 
                       & \textcolor{blue}{SecFFT}    & \textbf{\textcolor{blue}{0.96}} & \textbf{\textcolor{blue}{0.87}} & \textbf{\textcolor{blue}{0.00}} & \textbf{\textcolor{blue}{0.13}} & \textbf{\textcolor{blue}{0.94}} & \textbf{\textcolor{blue}{0.88}} \\ \hline
\end{tabular}
}
\vspace{1em}
\begin{tablenotes}
\scriptsize
\item ``Acc." stands for Accuracy, ``Rec." for Recall, ``FPR" for False Positive Rate, ``FNR" for False Negative Rate, ``AUC" for Area Under Curve, and ``MCC" for Matthews Correlation Coefficient. The strategies are abbreviated as ``None" (No strategy), ``Size" (Size-limited strategy), and ``Angle" (Angle-limited strategy).
\end{tablenotes}
\label{tab:detect}
\end{table}

\newpage

\section{Responses to the Comments from Reviewer 4}

% comment12
\rcomment{
\color{red} Why does the section on "Instantaneous Attack Behavior Perception" use the chi-square distribution to calculate outlier differences instead of cosine similarity? The manuscript lacks an explanation for this choice.
}
\textbf{Response:} 
We appreciate the reviewer’s insightful feedback. The decision to use the chi-square distribution instead of cosine similarity is rooted in the nature of the feature distribution in the frequency domain. Cosine similarity, while useful for comparing the angle between two vectors, would not appropriately capture the frequency domain’s distributional features in our model, where the outlier differences are more pronounced in the low-frequency components rather than in directional changes. The chi-square distribution allows us to better distinguish between malicious updates, which tend to introduce subtle but consistent deviations in these low-frequency features, and benign updates. This approach enhances detection accuracy by weighting the significant deviations while minimizing the impact of noise in the higher-frequency components.

@@

% comment13
\rcomment{
\color{red} The manuscript uses inconsistent figure referencing styles (e.g., "Fig. 7" vs. "Figure 6"). Please standardize the citation format.
}
\textbf{Response:} 
Thank you for pointing out the inconsistency in figure referencing throughout the manuscript. We have carefully reviewed all figure references and standardized the citation format. Going forward, we have consistently used the term "Figure" when referencing figures, ensuring uniformity across the entire paper.

@@

\textbf{Federated learning hyperparameters were informed by prior studies and practical considerations:}
For the federated training aspect of our research, we relied on previous studies, including \cite{wei2023personalized}, \cite{ilhan2023scalefl}, and \cite{wu2023faster}, which suggested a participants range from 20 to 200. Considering the time cost, computational overhead, and  the effectiveness of experimental results, we selected the most suitable configuration for our experiments, optimizing both performance and resource use.

% comment15
\rcomment{
\color{red} Why is the condition $\zeta T$ set in the optimization problem in Section V.2? Clarification is needed.
}

Thank you for your suggestion.

% comment16
\rcomment{
\color{red} There are numerous instances of incorrect symbol usage throughout the manuscript. A thorough review and correction are necessary.
}
\textbf{Response:} 
Thank you for your valuable feedback regarding the incorrect symbol usage in the manuscript. We have conducted a thorough review and carefully corrected all instances of improper symbol usage to ensure accuracy and consistency throughout the paper.
